---
title: "p8105_hw1_hw2851"
output: github_document
---

```{r include = FALSE}
library(tidyverse)

```

# Problem 1

```{r}

set.seed(123)

samp_df = tibble(
  samp = rnorm(10, mean = 0),
  logical_vector = samp > 0,
  chara_vector = c("This", "is", "homework", "one", "from", "Renee", "This", "is", "a", "homework"),
  fac_vector = factor(c("A", "A", "A", "B", "B", "B", "B", "C", "C", "C"))
)
```
The mean of samples drawn from the normal distribution is `r mean(pull(samp_df, samp))`.
The mean of the logical vector is `r mean(pull(samp_df, logical_vector))`.
The mean of the character vector is `r mean(pull(samp_df, chara_vector ))`.
The mean of the factor vector is `r mean(pull(samp_df, fac_vector))`.


```{r}
as.numeric(pull(samp_df,samp))
as.numeric(pull(samp_df,logical_vector))
as.numeric(pull(samp_df,chara_vector))
as.numeric(pull(samp_df,fac_vector))
```
The mean of the numeric vector, logical vector can be calculated directly but not character vector and factor vector. This can be partially explained by the as.numeric() cast result: there is no reasonable way to cast the character vector as a numeric vector, thus we also cannot take its mean. 
However, although as.numeric() works for the factor vector, we still cannot take its mean. This is because factors are stored as numeric variable with their level internally -- they are not scalar, thus mean() cannot be applied on a factor vector.

# Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```
The data penguins is a data frame including the following columns: `r names(penguins)`. One sample from the data frame is as follows: `r penguins[10,]`.
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean of the flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm), na.rm = TRUE) + geom_point(aes(color = species), na.rm = TRUE)
ggsave("penguins-scatter-plot.pdf")
```
